\textit{Supplemental figures for}: A Gaussian process model of human electrocorticographic data

### 2020-03-09 paper/supporting_information.tex
editing supplement [WIP, does not compile]

@@

\begin{figure}[b!]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_1}
\caption{\textbf{Reconstruction quality for Datasets 1 and 2.}
  \textbf{A. Distributions of correlations between observed versus
    reconstructed activity by electrode, for Dataset 1.} The split
  violin plot reflects the same data as Figure~3A, presented here for
  comparison.  \textbf{B. Distributions of correlation between
    observed versus reconstructed activity by electrode, for Dataset
    2.}  The left-most split violin plot (``Within'') reflects the
  same data as Figure~3B, presented here for comparison.  The
  ``Across'' plot reflects the same analyses, but limited to models
  that were trained and tested on \textit{different} Dataset 2
  experiments.  The ``All'' plot reflects the same analyses, but
  including models that were trained and tested on both of the Dataset
  2 experiments.  All plots: the dark gray distributions denote
  across-subject correlations (model trained on all but one patient
  and tested on the held-out patient), and the medium gray
  distributions denote within-subject correlations (model trained on
  all but one electrode from one patient, and tested on the held-out
  electrode).  The horizontal bars denote $t$-tests between the
  corresponding distributions (after $z$-transforming the
  correlations), and the white numbers reflect the distribution means.
  The symbols denote the corresponding $p$-values of those statistical
  tests.}
\label{fig:supplemental_1}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_2}
\caption{\textbf{Reconstruction quality for Dataset 2,
    Experiments 1 and 2.} \textbf{A. Distributions of correlations
    between observed versus reconstructed activity by electrode, for
    Experiment 1.}  Each split violin plot and horizontal bar is in
  the same format as the plots in Figure~\ref{fig:supplemental_1}.
  ``Within'' denotes within-subject correlations (model trained on all
  but one electrode from one patient, and tested on the held-out
  electrode); ``Across'' denotes across-subject correlations (model
  trained an all but one patient and tested on the held-out patient);
  ``All'' denotes a model trained on all data from all patients,
  except for one held-out electrode (and tested on the held-out
  electrode).  \textbf{B. Distributions of correlations between
    observed versus reconstructed activity by electrode, for
    Experiment 2.}  All of the plots and bars are in the same format
  as those in Panel A.}
\label{fig:supplemental_2}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_3}
\caption{\textbf{Reconstruction quality across all electrodes in two
      Dataset 2 experiments.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Experiment 1.}  Same format as Figure~3A and B, but reflects data shown
    in Figure~\ref{fig:supplemental_2}A (leftmost violin plot).
 \textbf{B. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Experiment 2.}  Same format as Figure~3A and B, but reflects
    data shown in Figure~\ref{fig:supplemental_2}B (leftmost violin
    plot).  \textbf{C.--D.  Reconstruction
      performance by location.} Each dot reflects the location of a
    single implanted electrode from Dataset 2, Experiment 1 (Panel C)
    or Dataset 2, Experiment 2 (Panel D).  The dot colors denote the
    average within-experiment (across-session)
    correlation, using the across-patient correlation model, between
    the observed and reconstructed activity at the given electrode
    location projected to the cortical surface~\citep{CombEtal19}.}
\label{fig:supplemental_3}
\end{figure}

@@

\begin{figure}[ptb]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_5}
\caption{\textbf{Most informative electrode locations by frequency
      and the networks involved.}
    \textbf{A.~Intersections across datasets for each frequency.}  Same format as Figure~6A, but
    using power at each frequency.
    \textbf{B.~Proportion of networks in most informative electrode locations by
    frequency.}  Pie graphs display the proportion of the 7 networks
  ~\citep{YeoEtal11} in the most informative locations by
  frequency, and are sized relative to the average reconstruction
  accuracy for each frequency. \textbf{C.~Terms associated with most informative
    electrode locations.}  The
    lists of terms display the top five Neurosynth
    terms~\citep{RubiEtal17} decoded from the corresponding brain
    maps, and colored according the frequency (see Panel
    E legend). \textbf{D.~Network parcellation from~\citep{YeoEtal11}.}
    Seven network parcellation as described
    in~\citep{YeoEtal11}. \textbf{E.~Most informative locations by
      frequency.} The inflated brain plot displays the locations of
    the most informative locations (Panel A), colored by frequency,
    and projected onto the cortical surface~\citep{CombEtal19}.}
\label{fig:supplemental_5}
\end{figure}

@@

\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}
\bibliography{CDL-bibliography/memlab}
\bibliographystyle{CSE}
% \newpage
% \renewcommand{\refname}{Supplemental references}
% \bibliography{memlab}

>>>>

\newcommand{\methods}{1}
\newcommand{\corrmaps}{2}
\newcommand{\freqs}{3}
\newcommand{\density}{4}
\newcommand{\infomap}{5}
\newcommand{\infomapfreqs}{6}

@@

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_1}
\caption{\textbf{Reconstruction quality across all electrodes in two
    ECoG datasets, broken down by experiment.}
  \textbf{A. Distributions of correlations between observed versus
    reconstructed activity by electrode, for Dataset 1.}  The
  across-patient distribution (black) reflects reconstruction accuracy
  (correlation) using a correlation model learned from all but one
  patient's data, and then applied to that held-out patient's data.
  The within-patient distribution (gray) reflects performance using a
  correlation model learned from the same patient who contributed the
  to-be-reconstructed electrode.  The split violin plot displays the
  same distributions shown in Figure~\corrmaps A.
  \textbf{B. Distributions of correlations for Dataset 2.}  The split
  violin plots are in the same format as those in Panel A.  The
  leftmost plot (``Within'') displays the same distributions shown in
  Figure~\corrmaps B.  All reconstructions reflected in the
  distribution were carried out using a model trained and tested using
  data from the same experiment.  The middle plots (``Across'')
  reflect reconstructions trained and tested using data from different
  experiments.  The rightmost plot (``All'') reflect reconstructions
  obtained using models trained and tested on data from both
  experiments.  The black distributions reflect models trained and
  tested across patients (analogous to the black histograms in
  Figure~\corrmaps) and the gray distributions reflect models trained
  and tested within patient (analogous to the gray histograms in
  Figure~\corrmaps).  The dark gray significance bars reflect
  paired-sample $t$-tests comparing the ($z$-transformed)
  reconstruction accuracy for each electrode obtained within versus
  across patients.  The black significance bars reflect paired-sample
  $t$-tests comparing the across-patient reconstruction accuracies
  across datasets.  The light gray significance bars reflect
  paired-sample $t$-tests comparing the within-patient reconstruction
  accuracies across datasets.  The symbols denote the corresponding
  $p$-values of those statistical tests.}
\label{fig:supplemental_1}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_2}
\caption{\textbf{Reconstruction quality for Dataset 2, Experiments 1
    and 2.}  \textbf{A. Distributions of correlations between observed
    versus reconstructed activity by electrode, for Dataset 2
    (Experiment 1).}  The plots are in the same format as
  Figure~\ref{fig:supplemental_1}B, but reflect data only from
  Experiment 1 in Dataset 2.  \textbf{A. Distributions of correlations between observed
    versus reconstructed activity by electrode, for Dataset 2
    (Experiment 2).  The plots are in the same format as Panel A, but
    reflect data only from Experiment 2 in Dataset 2.}} 
\label{fig:supplemental_2}
\end{figure}

%JRM STOPPED HERE
\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_3}
\caption{\textbf{Reconstruction quality across all electrodes, broken
    down by Dataset 2 experiment.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Dataset 1.}  The across-patient distribution (black) reflects
    reconstruction accuracy (correlation) using a correlation model
    learned from all but one patient's data, and then applied to that
    held-out patient's data.  The within-patient distribution (gray)
    reflects performance using a correlation model learned from the same
    patient who contributed the to-be-reconstructed electrode.
    \textbf{B. Distributions of correlations for Dataset 2.}  This
    panel is in the same format as Panel A, but reflects results
    obtained from Dataset 2.  The histograms aggregate data across
    both Dataset 2 experiments; for results broken down by experiment
    see Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction
      performance by location.} The colors denote the average across-session
    correlation, using the across-patient correlation model, between
    the observed and reconstructed activity at the given electrode
    location projected to the cortical surface~\citep{CombEtal19}.}

\caption{\textbf{Reconstruction quality across all electrodes in two
      Dataset 2 experiments.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Experiment 1.}  Same format as Figure~3A and B, but reflects data shown
    in Figure~\ref{fig:supplemental_2}A (leftmost violin plot).
 \textbf{B. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Experiment 2.}  Same format as Figure~3A and B, but reflects
    data shown in Figure~\ref{fig:supplemental_2}B (leftmost violin
    plot).  \textbf{C.--D.  Reconstruction
      performance by location.} Each dot reflects the location of a
    single implanted electrode from Dataset 2, Experiment 1 (Panel C)
    or Dataset 2, Experiment 2 (Panel D).  The dot colors denote the
    average within-experiment (across-session)
    correlation, using the across-patient correlation model, between
    the observed and reconstructed activity at the given electrode
    location projected to the cortical surface~\citep{CombEtal19}.}
\label{fig:supplemental_3}
\end{figure}

@@

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_5}
\caption{\textbf{Most informative electrode locations by frequency
      and the networks involved.}
    \textbf{A.~Intersections across datasets for each frequency.}  Same format as Figure~6A, but
    using power at each frequency.
    \textbf{B.~Proportion of networks in most informative electrode locations by
    frequency.}  Pie graphs display the proportion of the 7 networks
  ~\citep{YeoEtal11} in the most informative locations by
  frequency, and are sized relative to the average reconstruction
  accuracy for each frequency. \textbf{C.~Terms associated with most informative
    electrode locations.}  The
    lists of terms display the top five Neurosynth
    terms~\citep{RubiEtal17} decoded from the corresponding brain
    maps, and colored according the frequency (see Panel
    E legend). \textbf{D.~Network parcellation from~\citep{YeoEtal11}.}
    Seven network parcellation as described
    in~\citep{YeoEtal11}. \textbf{E.~Most informative locations by
      frequency.} The inflated brain plot displays the locations of
    the most informative locations (Panel A), colored by frequency,
    and projected onto the cortical surface~\citep{CombEtal19}.}
\label{fig:supplemental_5}
\end{figure}

@@

\clearpage
\newpage
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}
\bibliography{CDL-bibliography/memlab}
\bibliographystyle{CSE}
% \newpage
% \renewcommand{\refname}{Supplemental references}
% \bibliography{memlab}
